Cover letter for the original IJRR submission

### 2017-09-29 body/results.tex
octree environment
Review paper according to reviewers suggestions

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this section we present some of the results obtained with our planner. The complete sequences are shown in the companion video.
Specifically, we demonstrate the planner for two legged robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
Finally, a last example suggests possible applications to dexterous manipulation.

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation (ms) & Static equilibrium (ms) & Collision (ms) & Inverse Kinematics (ms) & Total generation time (ms) & Time per step (ms)\\
 \hline
   Stairs (18) 	& 5 -- \textbf{6} --  18 		 & 13 --  \textbf{32} -- 329   	& 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{15} \\
   Standing (24)& 65 -- \textbf{1086} --  5227   & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 371 --  \textbf{2257} -- 7671 & \textbf{94}  \\
   Car (86)& 320 -- \textbf{6971} --  44002 & 409 --  \textbf{1766} -- 14752   	& 297 -- \textbf{1187} -- 8483 & 3154 --  \textbf{15323} -- 165541 & 5834 --  \textbf{31391} -- 281000 & \textbf{365}\\
   Rubble (82)& 37 -- \textbf{573} --  1685 & 583 --  \textbf{2714} -- 9459 & 491 --  \textbf{1971} -- 6273 & 269 --  \textbf{706} -- 3118 & 1811 --  \textbf{7195} -- 23241 & \textbf{86} \\
   Race (134)& 14 -- \textbf{51} --  125 & 455 --  \textbf{1359} -- 21045   & 397 --  \textbf{923} -- 9924 & 228 --  \textbf{471} -- 5415 & 1436 --  \textbf{3343} -- 41446 & \textbf{25}
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process (not all parts are timed,
thus the average total computation time is higher than the sum of each part). The last
column indicates the average time necessary to compute one contact transition. }
\label{tab:requestime}
\quad
\end{table*}

@@

\subsection{Validation of the contact plans} \label{sec:valid}
To validate our plans, we either use the framework of \cite{Carpentier2016}, or our own implementation of a $\mathcal{P}_3$ solver (Appendix~\ref{app:optim}).
The companion video shows the obtained motions.

\subsection{Comparison with previous work} \label{sec:compa}
%~ Few contributions provided computation times on the complete problem. To provide a completely fair comparison, it would be required to compare the methods on the same computers and exact same scenarios, which is not possible because 
%~ the source code of the other methods is often not available. %, necessary to provide comparison between our approaches. 
We did our best to provide a fair comparison of the computation complexity of our method with the state of the art. 
%Few contributions provided computation times on the complete problem. 
However existing benchmarks for motion planning algorithms~\cite{moll2014extensible} do not yet encompass contact planning.
Moreover, the source code of the previous methods of the state of the art is often not available.
Providing a fair comparison with the algorithms performing on the same computer and on the same scenarios is yet out of reach.
A step in this direction is the open-source release of our source code (see Appendix~\ref{app:hpp}) that allows any reader to reproduce our results.
Furthermore, $\mathcal{P}_3$ remains challenging in the presence of obstacles. The only valid scenarios addressed completely in previous works are thus the stair-climbing scenarios of different heights proposed by Hauser in \cite{Hauser06usingmotion}, and the table-egress scenario by Escande et al. in~\cite{DBLP:conf/iser/EscandeKMG08}, which we consider to be of similar complexity with respect to the car-egress scenario (we did not consider the stairs in the scene). Both scenarios are tested with HRP-2.

>>>>

% !TEX root =  ../main_tro.tex
\section{Results}
\label{sec:results}
In this section we present some of the results obtained with our planner. The complete sequences are shown in the companion video.
Specifically, we demonstrate the planner for two legged robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
Finally, a last example suggests possible applications to dexterous manipulation.

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation (ms) & Static equilibrium (ms) & Collision (ms) & Inverse Kinematics (ms) & Total generation time (ms) & Time per step (ms)\\
 \hline
   Stairs (18) 	& 5 -- \textbf{6} --  18 		 & 13 --  \textbf{32} -- 329   	& 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{15} \\
   Standing (24)& 65 -- \textbf{1086} --  5227   & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 371 --  \textbf{2257} -- 7671 & \textbf{94}  \\
   Car (86)& 320 -- \textbf{6971} --  44002 & 409 --  \textbf{1766} -- 14752   	& 297 -- \textbf{1187} -- 8483 & 3154 --  \textbf{15323} -- 165541 & 5834 --  \textbf{31391} -- 281000 & \textbf{365}\\
   Rubble (82)& 37 -- \textbf{573} --  1685 & 583 --  \textbf{2714} -- 9459 & 491 --  \textbf{1971} -- 6273 & 269 --  \textbf{706} -- 3118 & 1811 --  \textbf{7195} -- 23241 & \textbf{86} \\
   Race (134)& 14 -- \textbf{51} --  125 & 455 --  \textbf{1359} -- 21045   & 397 --  \textbf{923} -- 9924 & 228 --  \textbf{471} -- 5415 & 1436 --  \textbf{3343} -- 41446 & \textbf{25}
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process (not all parts are timed,
thus the average total computation time is higher than the sum of each part). The last
column indicates the average time necessary to compute one contact transition. The Collision column times includes the (negligeable) octree intersection operation necessary to retrieve the candidate samples.}
\label{tab:requestime}
\quad
\end{table*}

@@

\subsection{Validation of the contact plans} \label{sec:valid}
\adnote{I added the description of the simulations here, but I wonder whether this part should not be moved to the beginning of the Results section.}
To generate continuous movements from our contact plans we used either the framework proposed in \cite{Carpentier2016}, or our own implementation of a $\mathcal{P}_3$ solver (Appendix~\ref{app:optim}).
The resulting movements have been validated either on the real HRP-2 robot (details can be found in~\cite{Carpentier2016}), or with our dynamic simulator, based on a state-of-the-art algorithm~\cite{Kaufman2008}.
In the simulations we controlled the robot with a standard inverse-dynamics controller~\cite{DelPrete2015b}.
This controller tries to follow the given whole-body trajectories, giving higher priority to the center-of-mass and end-effectors tracking with respect to the joint tracking.
The controller also makes sure that the resulting contact forces lie inside the specified friction cones (we used a friction coefficient of 0.3), and that the joint position, velocity and torque limits are satisfied.
The companion video shows the obtained motions.

\subsection{Comparison with previous work} \label{sec:compa}
%~ Few contributions provided computation times on the complete problem. To provide a completely fair comparison, it would be required to compare the methods on the same computers and exact same scenarios, which is not possible because 
%~ the source code of the other methods is often not available. %, necessary to provide comparison between our approaches. 
We did our best to provide a fair comparison of the computation complexity of our method with the state of the art. 
%Few contributions provided computation times on the complete problem. 
However existing benchmarks for motion planning algorithms~\cite{moll2014extensible} do not yet encompass contact planning.
Moreover, the source code of the previous methods of the state of the art is often not available.
Providing a fair comparison with the algorithms performing on the same computer and on the same scenarios is yet out of reach.
A step in this direction is the open-source release of our source code (see Section~\ref{app:hpp}) that allows any reader to reproduce our results.
Furthermore, $\mathcal{P}_3$ remains challenging in the presence of obstacles. The only valid scenarios addressed completely in previous works are thus the stair-climbing scenarios of different heights proposed by Hauser in \cite{Hauser06usingmotion}, and the table-egress scenario by Escande et al. in~\cite{DBLP:conf/iser/EscandeKMG08}, which we consider to be of similar complexity with respect to the car-egress scenario (we did not consider the stairs in the scene). Both scenarios are tested with HRP-2.
